Ricci and transit times

### 2014-12-18 prep_figures/commute/commute-detail.Rmd

d5 <- get_results("../../results-rspr/commute-onesplit/123_45-1v5c.tsv")
d6 <- get_results("../../results-rspr/commute-onesplit/123_456-1v5c.tsv")
d <- d6

>>>>

d5 <- get_results("../../results-rspr/commute-onesplit/123_45-1v5c.tsv")
d6 <- get_results("../../results-rspr/commute-onesplit/123_456-1v5c.tsv")
d <- d5
